\documentclass[10pt, a4paper]{article}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{framed}
\usepackage{listings}

\colorlet{shadecolor}{blue!20}

\newcommand{\includecode}[3]{\lstinputlisting[caption=#1, label=#2]{#3}}

\begin{document}
\title{Linkit}
\author{Pierre Sugar\\
\texttt{pierre@sugaryourcoffee.de}}
\date{\today}
\maketitle

\begin{abstract}
\texttt{linkit} is a command line application that adds links to a web page that
is created and updated by \texttt{linkit}. Links as said can be added but also
updated and removed. It is possible to search links from the command line and
list them. \texttt{linkit} can check whether the links are still active and
list inactive links. Each link can have a category, tags and a discription. The
category is used to group links and the discription can be searched for but
tags a specifically used for searching for specific terms and topics.
\end{abstract}

\section{Project outline}
The programm runs from the command line. When provided a link \texttt{linkit}
will check whether the link exists and adds it to the web page. A link can be
anything that is accessible over an \texttt{URI}. That is web sites and files.

\begin{itemize}
  \item add a link
  \item update a link
  \item remove a link
  \item check if link is alive
  \item search link based on description and tags
  \item list all links
  \item invoke link from command line (should open web site or file)
\end{itemize}

\section{Source code management}
We organize the source in \texttt{Git} at 
\url{https://github.com/sugaryourcoffee/linkit}. We first create our project
with \texttt{Mix}, then we cd into the project directory, initialize our git
repository, do an initial commit and push the repository to \texttt{Github}.

\begin{verbatim}
$ mix new linkit
$ cd linkit
$ git init
$ git add .
$ git commit -am "initial commit"
$ git remote add origin git@github.com:sugaryourcoffee/linkit.git
$ git push -u origin master
$
\end{verbatim}

\section{Implement the Command Line Interface}
We write the test first for our command line interface to describe the
functions the command line interface actually should provide. We first 
describe the commands of \texttt{linkit}.

\begin{verbatim}
$ linkit add "http://elixir-lang.org"\
             --tag Elixir\
             --description "Home page of Elixir"
Added "http://elixir-lang.org"
$ linkit add "http://ruby-lang.org"\
             --tag Ruby\
             --description "Home of Ruby"
$ linkit update "http://elxir-lang.org"\
             --description "Home of Elixir"
Updated "http://elixir-lang.org" with description "Home of Elixir"
$ linkit delete "http://elixir-lang.org"
Deleted "http://elixir-lang.org"
$ linkit check "http://elixir-lang.com"
Check error: "http://elixir-lang.com" is not available
$ linkit list --tag "Elixir"
URL                      | Description   | Tags
-------------------------+---------------+-------
"http://elixir-lang.org" | Home of Elxir | Elixir
$ linkit call "http://elixir-lang.org"
$ linkit list
URL                      | Description   | Tags
-------------------------+---------------+-------
"http://elixir-lang.org" | Home of Elxir | Elixir
"http://ruby-lang.org"   | Home of Ruby  | Ruby   
\end{verbatim}

The test is shown in \ref{lst:cli-test} on page \pageref{lst:cli-test}.

\includecode{test/cli\_test.exs}{lst:cli-test}{files/cli_test.exs}

The implementation so far is in \ref{lst:cli} on page \pageref{lst:cli}.

\includecode{lib/linkit/cli.ex}{lst:cli}{files/cli.ex}

Now that the commands get parsed we want to process the commands. The help 
command is the easiest so we start with that. The help command just prints
the usage of \texttt{linkit} and then exits the application.

The next command we will process is the \texttt{add} command as without this
we cannot do anything with the application. In a first step we just save the
links to a file. The generation of the web page will follow later on when we
have implemented the other commands.

We first have to decide where the link-file lives. We could let the user 
decide about that. But we will take the approach to put the working directory
in the users home folder under \texttt{~/.syc/linkit/}. There we put all
application specific data. We call the link file \texttt{links}. So we don't 
have to hardcode this we want to make this configurable. The place for that is
the \texttt{config/config.exs}. 

\includecode{config/config.exs}{lst:config}{files/config.exs}

The \texttt{add} function needs to check whether the \texttt{URI} is already
in the \texttt{links}-file. So we read the file and check whether the link is
already there. If not we add the link otherwise we ask whether we should update
the link with the new \texttt{tags} and \texttt{description} if given.

To list the \texttt{URI}s the user invokes the \texttt{list} function. We read
the \texttt{link} file and print the contents in a nicely formatted table.

The \texttt{update} function we will implement in a similar way as the 
\texttt{add} function. We also check whether the link is available if not we 
ask the user whether to add it as a new link otherwise we update the link as 
intended.

When the \texttt{check} function is invoked we call the link and see whether it
returns a \texttt{Error 404: Not found} error. After all links have been 
checked we print a statistic about the checks. The \texttt{check} function is a
good candidate to use \texttt{Agent}s and run the checks in parallel.

The purpose of the \texttt{remove} link is basically after the \texttt{check}
function fails for a specific \texttt{link} we want to remove the dead link
from our \texttt{link} file.

As usual we will start with the tests which are shown in 
\ref{lst:cli-process-test} on page \pageref{lst:cli-process-test}.

\includecode{test/cli\_process\_test.exs}{lst:cli-process-test}
            {files/cli_process_test.exs}.

\end{document}
